Automatic Matching of Bullet Lands

### 2016-01-14 imaging-paper.Rnw
Reword mission statement

The primary goal in this type of forensic analysis is to identify these striation markings in an attempt to match two bullets. Since gun barrels should produce similar markings on bullets fired consecutively, the careful analysis of these surface images can help in determining whether two bullets are a match. This process has traditionally required forensic experts to perform the analysis, and required physical examination of the bullets.

@@

In this paper, we propose a framework which allows for the automatic analysis of the surface topologies of bullets, and the transcription of the individual characteristics into a 2D plotting framework. 
This allows for an objective and quantitative assessment of striae-based bullet matches.

>>>>

From a statistical standpoint, identification of the gun that fired the bullet(s) requires that we compare the probabilities of observing matching striae under the competing hypotheses that the gun fired, or did not fire, the crime scene bullet. If indeed the uniqueness assumption is plausible, the latter probability approaches zero.

@@

Here, we focus on the question of defining what constitutes a match, since there is no agreement in the forensics community. We propose a framework which allows for the automatic analysis of the surface topologies of bullets, and the transcription of the individual characteristics into a 2D plotting framework. 
This allows for an objective and quantitative assessment of striae-based bullet matches.
